---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
set.seed(101315)
```

# gMCPtest

## Overview

Compute weights for each intersection hypothesis in the closure of a graph-based multiple testing procedure.

## Installation

There is no CRAN version of this package, so you must install the development version directly from github.

```{r, eval = FALSE}
# Install development version from GitHub
remotes::install_github("anthonypileggi/gMCPtest")
```

## Getting Started

Suppose `w` represents a vector of weights defining how much of the overall alpha is initially reserved for each hypothesis.  Assume that `G` is a graph represented as a matrix of transition weights, where element `(i, j)` defines how much of the $\alpha$ from hypothesis `i` is passed to hypothesis `j`.  Then we can compute the weights for each intersection hypothesis using:

```{r, eval = T}
library(gMCPtest)
library(magrittr)
```

```{r, eval = F}
generate_weights(G, w)
```

## Examples

### Example 1

Following the example of [Bretz et al. (2011)](https://onlinelibrary.wiley.com/doi/10.1002/bimj.201000239) assume a primary family of hypotheses $F_1 = \{H_1, H_2\}$ and a secondary family $F_2 = \{H_3, H_4\}$ and suppose a strict hierarchy such that the secondary endpoints $H_3$ and $H_4$ will only be assessed if the primary endpoints $H_1$ and $H_2$ are rejected, respectively.

```{r, eval = T}
G <- matrix(
  c(0,0,1,0,
    0,0,0,1,
    0,1,0,0,
    1,0,0,0), 
  nrow = 4,
  byrow = TRUE
)
w <- c(1/2, 1/2, 0, 0)
generate_weights(G, w) %>%
  print_weights()
```

### Example 2
```{r, eval = T}
# equal weight for all hypotheses
w <- rep(1/4, 4)
generate_weights(G, w) %>%
  print_weights()
```


### Example 3

Consider 3 hypotheses tested successively.

```{r, eval = T}
G <- matrix(
  c(0,1,0,
    0,0,1,
    1,0,0), 
  nrow = 3,
  byrow = TRUE
)
w <- c(1, 0 ,0)
generate_weights(G, w) %>%
  print_weights()
```


## References

- [Graphical approaches for multiple comparison procedures using weighted Bonferroni, Simes, or parametric tests (Bretz et al., 2011)](https://onlinelibrary.wiley.com/doi/10.1002/bimj.201000239)
- [gMCP](https://github.com/kornl/gMCP) package -- this gMCPtest package is really just providing access to one function from gMCP, the [`generateWeights()`](https://github.com/kornl/gMCP/blob/master/pkg/gMCP/R/generateWeights.R) function.
